Moral Foundations of U.S. Political News Organizations

### 2019-02-25 pilot_manuscript.Rmd
added bit to search NYtimes

>>>>

```{r NYTimes, eval = F, include = F}

library(rvest)
####NY Times####
#Specifying the url for desired website to be scrapped
url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'

#Reading the HTML code from the website - headlines
webpage <- read_html(url)
headline_data = html_nodes(webpage,'a')

urlslist = unlist(attr_data)
urlslist = urlslist[grep(".html", urlslist)]
urlslist = unique(urlslist)
urlslist

#paste NY on front
urlslist = paste("https://www.nytimes.com", urlslist, sep = "")

  ##pull the specific nodes
  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
